\textbf{Computational Fuzzy Extractors}

### 2013-04-05 CompFuzzExt.tex
Adding references to computational extractors

%to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.  This string $\recout$ is  required to have high HILL entropy even conditioned on $s$. Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
By considering a computational secrecy requirement, we are able to construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{A trivial construction is possible for very high entropy sources.  An information-theoretic fuzzy extractor can be used to derive a key $r$ and $r$ can be expanded using a pseudorandom generator.  However, when the source is low entropy, the entropy loss due to the information theoretic fuzzy extractor may make it impossible to securely run a pseudorandom generator.  We present a comparison between the two methods in \secref{sec:prg based comparison}}. % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).  
Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.  
%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application} 
Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.  To apply the LWE assumption, we correct errors of a random linear code which limits our decoding algorithm to reconciling a logarithmic number of differences.

>>>>

%to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.  This string $\recout$ is  required to have high HILL entropy even conditioned on $s$. Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
Computational extractors~\cite{krawczyk2010cryptographic, dachman2012computational} have the same goal in the setting without errors.  One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.  In particular, one technique is ``extract-then-expand'', where the output of a randomness extractor is stretched using a pseudorandom generator.  This construction is only possible if the entropy losses due to a secure sketch and information-theoretic extraction leave enough truly random bits.  We ask if a better solution is possible by making the entire process ``computational''.

By considering a computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{A trivial construction is possible for very high entropy sources.  An information-theoretic fuzzy extractor can be used to derive a key $r$ and $r$ can be expanded using a pseudorandom generator.  However, when the source is low entropy, the entropy loss due to the information theoretic fuzzy extractor may make it impossible to securely run a pseudorandom generator.  We present a comparison between the two methods in \secref{sec:prg based comparison}}. % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).  
Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.  
%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application} 
Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.  To apply the LWE assumption, we correct errors of a random linear code which limits our decoding algorithm to reconciling a logarithmic number of differences.
